Supporting information for ``How environmental drivers of synchrony interact''

### 2022-01-14 Paper/SupMat.Rnw
working on Methods and Results

resloc<-"../Results/Kelp_DataAfterSuperBasicCleaning/"
kelp_SB<-readRDS(paste0(resloc,"Kelp_Quarterly_CleanedSuperBasic.Rds"))
resloc<-"../Results/Kelp_DataAfterMoreInvolvedCleaning/"
kelp_MI<-readRDS(paste0(resloc,"Kelp_Quarterly_CleanedMoreInvolved.Rds"))
@

@@

\section{Details of statistical methods}

@@

\begin{figure}[!h]
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_MainPlot_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_MainPlot_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_MainPlot_ForMS.pdf}
\caption[Extension of main text Fig. \ref{MT-fig:SummaryKelpFig}]{Same format as Fig. \ref{MT-fig:SummaryKelpFig} of the main text, but including not only results
for the first central CA region (a-c) and the southern CA region (d-f), but also results from the 
second central CA region (g-i).}\label{fig:SummaryKelpFig_SM_lag4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_ExplainDirectMoran_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_ExplainDirectMoran_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_ExplainDirectMoran_ForMS.pdf}
\caption[Extension of main text Fig. \ref{MT-fig:directMoran}]{Same format as Fig. \ref{MT-fig:directMoran} of the main text, but including not only results
for the first central CA region (a-o) and the southern CA region (p-dd), but also results from the 
second central CA region (ee-ss).}\label{fig:directMoran_SM_lag4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_ExplainInteractingMoran_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_ExplainInteractingMoran_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_ExplainInteractingMoran_ForMS.pdf} 
\caption[Extension of main text Fig. \ref{MT-fig:indirectMoran}]{Same format as Fig. \ref{MT-fig:indirectMoran} of the main text, but including not only results
for the first central CA region (a-o) and the southern CA region (p-dd), but also results from the 
second central CA region (ee-ss).}\label{fig:indirectMoran_SM_lag4}
\end{figure}

@@

\clearpage
\newpage

>>>>

resloc<-"../Results/Kelp_DataAfterSuperBasicCleaning/"
kelp_SB<-readRDS(paste0(resloc,"Kelp_Quarterly_CleanedSuperBasic.Rds"))
resloc<-"../Results/Kelp_DataAfterMoreInvolvedCleaning/"
kelp_MI<-readRDS(paste0(resloc,"Kelp_Quarterly_CleanedMoreInvolved.Rds"))

resloc<-"../Results/Kelp_SpectralDecompResults/"
CCA1l4<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal1_KelpLag4.Rds"))
CCA2l4<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal2_KelpLag4.Rds"))
SBl4<-readRDS(paste0(resloc,"RegionalAnalysis_SoCal_KelpLag4.Rds"))
CCA1l8<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal1_KelpLag8.Rds"))
CCA2l8<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal2_KelpLag8.Rds"))
SBl8<-readRDS(paste0(resloc,"RegionalAnalysis_SoCal_KelpLag8.Rds"))
CCA1l12<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal1_KelpLag12.Rds"))
CCA2l12<-readRDS(paste0(resloc,"RegionalAnalysis_CentCal2_KelpLag12.Rds"))
SBl12<-readRDS(paste0(resloc,"RegionalAnalysis_SoCal_KelpLag12.Rds"))
@

@@

@@

\begin{figure}[!h]
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_MainPlot_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_MainPlot_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_MainPlot_ForMS.pdf}
\caption[Extension of main text Fig. \ref{MT-fig:SummaryKelpFig}]{Same format as Fig. \ref{MT-fig:SummaryKelpFig} of the main text, but including not only results
for the CCA1 region (a-c) and the SB region (d-f), but also results from the 
CCA2 region (g-i).}\label{fig:SummaryKelpFig_SM_lag4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_ExplainDirectMoran_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_ExplainDirectMoran_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_ExplainDirectMoran_ForMS.pdf}
\caption[Extension of main text Fig. \ref{MT-fig:directMoran}]{Same format as Fig. \ref{MT-fig:directMoran} of the main text, but including not only results
for the CCA1 region (a-o) and the SB region (p-dd), but also results from the 
CCA2 region (ee-ss).}\label{fig:directMoran_SM_lag4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal1_KelpLag4_ExplainInteractingMoran_ForMS.pdf}
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_SoCal_KelpLag4_ExplainInteractingMoran_ForMS.pdf} \\
\includegraphics[width=.5\textwidth]{../Results/Kelp_SpectralDecompResults/RegionalAnalysis_CentCal2_KelpLag4_ExplainInteractingMoran_ForMS.pdf} 
\caption[Extension of main text Fig. \ref{MT-fig:indirectMoran}]{Same format as Fig. \ref{MT-fig:indirectMoran} of the main text, but including not only results
for the CCA1 region (a-o) and the SB region (p-dd), but also results from the 
CCA2 region (ee-ss).}\label{fig:indirectMoran_SM_lag4}
\end{figure}

@@

\clearpage

\begin{table}[!h]
\caption{Regression coefficients used to parameters (\ref{MT-main_model_1})-(\ref{MT-main_model_4}) of the main text for each 
of our three regions. All values rounded to two decimal places.}\label{tab:regcoefs}
\begin{center}
\begin{tabular}{r|l|l|l|l|l}
 & $p_0^{(1)}$ & $p_1^{(1)}$ & $p_0^{(2)}$ & $b_1,b_2,\ldots,b_n$ & $R^2$\\
 \hline
%n=4
CCA1, $n=4$ & \Sexpr{round(unname(CCA1l4[6]),2)} & \Sexpr{round(unname(CCA1l4[7]),2)} & \Sexpr{round(unname(CCA1l4[8]),2)} & \Sexpr{paste0(round(unname(CCA1l4[2:5]),2),collapse=",")} & \Sexpr{round(unname(CCA1l4[1]),2)} \\
CCA2, $n=4$ & \Sexpr{round(unname(CCA2l4[6]),2)} & \Sexpr{round(unname(CCA2l4[7]),2)} & \Sexpr{round(unname(CCA2l4[8]),2)} & \Sexpr{paste0(round(unname(CCA2l4[2:5]),2),collapse=",")} & \Sexpr{round(unname(CCA2l4[1]),2)} \\
SB, $n=4$ & \Sexpr{round(unname(SBl4[6]),2)} & \Sexpr{round(unname(SBl4[7]),2)} & \Sexpr{round(unname(SBl4[8]),2)} & \Sexpr{paste0(round(unname(SBl4[2:5]),2),collapse=",")} & \Sexpr{round(unname(SBl4[1]),2)} \\
%n=8
CCA1, $n=8$ & \Sexpr{round(unname(CCA1l8[10]),2)} & \Sexpr{round(unname(CCA1l8[11]),2)} & \Sexpr{round(unname(CCA1l8[12]),2)} & \Sexpr{paste0(round(unname(CCA1l8[2:9]),2),collapse=",")} & \Sexpr{round(unname(CCA1l8[1]),2)} \\
CCA2, $n=8$ & \Sexpr{round(unname(CCA2l8[10]),2)} & \Sexpr{round(unname(CCA2l8[11]),2)} & \Sexpr{round(unname(CCA2l8[12]),2)} & \Sexpr{paste0(round(unname(CCA2l8[2:9]),2),collapse=",")} & \Sexpr{round(unname(CCA2l8[1]),2)} \\
SB, $n=8$ & \Sexpr{round(unname(SBl8[10]),2)} & \Sexpr{round(unname(SBl8[11]),2)} & \Sexpr{round(unname(SBl8[12]),2)} & \Sexpr{paste0(round(unname(SBl8[2:9]),2),collapse=",")} & \Sexpr{round(unname(SBl8[1]),2)} \\
%n=12
CCA1, $n=12$ & \Sexpr{round(unname(CCA1l12[14]),2)} & \Sexpr{round(unname(CCA1l12[15]),2)} & \Sexpr{round(unname(CCA1l12[16]),2)} & \Sexpr{paste0(round(unname(CCA1l12[2:13]),2),collapse=",")} & \Sexpr{round(unname(CCA1l12[1]),2)} \\
CCA2, $n=12$ & \Sexpr{round(unname(CCA2l12[14]),2)} & \Sexpr{round(unname(CCA2l12[15]),2)} & \Sexpr{round(unname(CCA2l12[16]),2)} & \Sexpr{paste0(round(unname(CCA2l12[2:13]),2),collapse=",")} & \Sexpr{round(unname(CCA2l12[1]),2)} \\
SB, $n=12$ & \Sexpr{round(unname(SBl12[14]),2)} & \Sexpr{round(unname(SBl12[15]),2)} & \Sexpr{round(unname(SBl12[16]),2)} & \Sexpr{paste0(round(unname(SBl12[2:13]),2),collapse=",")} & \Sexpr{round(unname(SBl12[1]),2)} \\
\end{tabular}
\end{center}
\end{table}
